Can Cultural Transmission Explain The Evolution of Cooperative Behavior?

### 2020-04-23 ms/main.tex
more formatting in last section

In this case horizontal transmission can not occur as a result of interaction.  
Then, eq.~\ref{eq:unequal_transmission} becomes:
\begin{equation} 
\begin{split} \label{eq:horizontal_transmission_from_population}
c\cdot(1-T_B) < & (T_A-T_B)(1+b\tilde{p})  
\end{split}
\end{equation}

Therefore, since $c>0$, cooperation will not take over the population (and furthermore will become extinct) if $T_A\leq T_B$.
When $T_A > T_B$ eq.~\ref{eq:horizontal_transmission_from_population} becomes:
\begin{equation} 
\begin{split} \label{eq:horizontal_transmission_from_population_reorder}
\tilde{p} & > \frac{c\cdot(1-T_B)+T_B-T_A}{b\cdot(T_A-T_B)}
\end{split}
\end{equation}
Hence, cooperation will take over the population when when eq.~\ref{eq:horizontal_transmission_from_population_reorder} is satisfied, that is if $\tilde{p}$ is above the threshold on the RHS. 
When $\tilde{p}$ is equal to eq.~\ref{eq:horizontal_transmission_from_population_reorder} RSH the frequency of phenotype A do not change. Denote $\tilde{p}^{*}$:
\begin{equation} 
\begin{split} \label{eq:horizontal_transmission_from_population_equilibrium}
\tilde{p}^{*} & = \frac{c\cdot(1-T_B)+T_B-T_A}{b\cdot(T_A-T_B)} .
\end{split}
\end{equation}
Therefore, $\tilde{p}^{*}$ is the third equilibrium in this system.
Specifically, a sufficient condition for cooperation fixation is found by setting the the equilibrium $\tilde{p}^*$  to be negative:
\begin{equation} 
\begin{split} \label{eq:sufficient_horizontal_transmission_from_population}
c < &\, \frac{T_A-T_B}{1-T_B}  
\end{split}
\end{equation}

@@

So far, we assumed that $v=1$. The next section discuss the effect of oblique transmission: transmission from non-parental adults.

@@

\textbf{Result 2: Oblique and horizontal transmission of cooperation.} The frequency of phenotype $A$ among adults increases if $p'>p$.
From eq.~\ref{eq:nextgen_parents_oblique_only}, this occurs when:
\begin{equation} \label{eq:oblique_only_result}
T_A>T_B  
\end{equation}

>>>>

In this case horizontal transmission can not occur as a result of interaction.  
Then, eq.~\ref{eq:unequal_transmission} becomes
\begin{equation} 
\begin{split} \label{eq:horizontal_transmission_from_population}
c\cdot(1-T_B) < & (T_A-T_B)(1+b\tilde{p}).
\end{split}
\end{equation}

Therefore, since $c>0$, cooperation will not take over the population (and furthermore will become extinct) if $T_A\leq T_B$.
When $T_A > T_B$ eq.~\ref{eq:horizontal_transmission_from_population} becomes
\begin{equation} 
\begin{split} \label{eq:horizontal_transmission_from_population_reorder}
\tilde{p} & > \frac{c\cdot(1-T_B) - (T_A-T_B)}{b\cdot(T_A-T_B)}.
\end{split}
\end{equation}
Hence, cooperation will evolve if $\tilde{p} > \tilde{p}^{*}$, which is given by
\begin{equation} 
\begin{split} \label{eq:horizontal_transmission_from_population_equilibrium}
\tilde{p}^{*} & = \frac{c\cdot(1-T_B)}{b\cdot(T_A-T_B)} - \frac{1}{b}.
\end{split}
\end{equation}
A sufficient condition for evolution of cooperation is, then,
\begin{equation} 
\begin{split} \label{eq:sufficient_horizontal_transmission_from_population}
\frac{T_A-T_B}{1-T_B} > &\ c.  
\end{split}
\end{equation}

@@

We now discuss the effect of oblique transmission, i.e. transmission from non-parental adults.

@@

\textbf{Result 2: Oblique and horizontal transmission of cooperation.} The frequency of phenotype $A$ among adults increases if $p'>p$.
From eq.~\ref{eq:nextgen_parents_oblique_only}, this occurs when:
\begin{equation} \label{eq:oblique_only_result}
T_A>T_B. 
\end{equation}
% TODO proof.
